\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[usenames]{color}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}

\hypersetup{
  urlbordercolor = {1 1 1}
}

\leftmargin=0.25in
\oddsidemargin=0.25in
\textwidth=6.0in
\topmargin=-0.25in
\textheight=9.25in

\raggedright

\pagenumbering{arabic}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
% DEFINITIONS FOR RESUME

\newenvironment{changemargin}[2]{%
  \begin{list}{}{%
    \setlength{\topsep}{0pt}%
    \setlength{\leftmargin}{#1}%
    \setlength{\rightmargin}{#2}%
    \setlength{\listparindent}{\parindent}%
    \setlength{\itemindent}{\parindent}%
    \setlength{\parsep}{\parskip}%
  }%
  \item[]}{\end{list}
}

\newcommand{\lineover}{
	\begin{changemargin}{-0.05in}{-0.05in}
		\vspace*{-8pt}
		\hrulefill \\
		\vspace*{-2pt}
	\end{changemargin}
}

\newcommand{\header}[1]{
	\begin{changemargin}{-0.5in}{-0.5in}
		\scshape{#1}\\
  	\lineover
	\end{changemargin}
}

\newcommand{\contact}[5]{
	\begin{changemargin}{-0.5in}{-0.5in}
		\begin{center}
			{\Large \scshape {#1}}\\ \smallskip
			{#2}\\ \smallskip 
			{#3}\\ \smallskip
			{#4}\\ \smallskip
			{#5}\\ \smallskip
		\end{center}
	\end{changemargin}
}

\newenvironment{body} {
	\vspace*{-16pt}
	\begin{changemargin}{-0.25in}{-0.5in}
  }	
	{\end{changemargin}
}	

\newcommand{\school}[4]{
	\textbf{#1} \hfill \emph{#2\\}
	#3\\ 
	#4\\
}

% END RESUME DEFINITIONS

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Name
\contact{Krish Perumal}{Unit No 018-B, 60 Harbord Street, Toronto, Ontario M5S 1G2, Canada}{+1 647 838 7824}{[myfirstname] [at] cs [dot] toronto [dot] edu}{\url{http://www.cs.toronto.edu/~krish}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Objective
% \header{Objective}
% 
% \begin{body}
% 	\vspace{14pt}
% 	To get a job
% \end{body}
% 
% \smallskip


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
\header{Education}

\begin{body}
	\vspace{14pt}
	\textbf{M.Sc. Computer Science}{} \hfill \emph{Sept 2014 - present}{} \\
    \textbf{(Specialization in Computational Linguistics)} \\
	\emph{University of Toronto}, Toronto, Ontario, Canada{} \\
    \emph{Supervisor: Prof. Graeme Hirst} (\url{http://www.cs.toronto.edu/~gh}) \\
	\smallskip
	\vspace{14pt}
	\textbf{M.Sc.(Tech.)* Information Systems --- GPA 9.22/10}{} \hfill \emph{Aug 2008 - Jul 2012}{} \\
	\emph{Birla Institute of Technology and Science, Pilani}, Rajasthan, India{} \\
	\smallskip
	\scriptsize{*This is an undergraduate degree equivalent to the Bachelor of Engineering awarded at other Indian universities} \\
\end{body}

\smallskip


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Experience
\header{Work Experience}

\begin{body}
	\vspace{14pt}
	\textbf{Research Assistant}, \emph{Ubiquitous Knowledge Processing Lab} \hfill \emph{Apr 2013 - Mar 2014} \\
	\emph{Technische Universität Darmstadt, Darmstadt, Germany} \\
	\emph{Advisor}: Prof. Dr. Iryna Gurevych (\url{http://www.ukp.tu-darmstadt.de/people/gurevych}) \\
	\emph{Projects}: Automatic mining and extraction of arguments for intelligent essay writing assistance \\ 
	\hspace{42pt} Language-independent classification of edits in Wikipedia \\
	
	\medskip
	
	\textbf {Research Assistant}, \emph{Search and Information Extraction Lab} \hfill \emph{Jul 2012 - Feb 2013} \\
	\emph{International Institute of Information Technology, Hyderabad, India} \\
	\emph{Advisor}: Prof. Vasudeva Varma (\url{http://faculty.iiit.ac.in/~vv/Home.html}) \\
	\emph{Project}: Cross Lingual Information Access \\
	Developed modules/plugins for a cross-lingual web search engine for Indian languages (Apache Nutch framework) called Sandhan (\url{http://www.tdil-dc.in/sandhan}).
	This project is funded by the Government of India.
	
	\medskip
	
	\textbf {Intern}, \emph{NetApp Inc., Bangalore, India} \hfill \emph{Jan - Jun 2012} \\
	\emph{Advisor}: Dr. Jayanta Basak (Member Technical Staff, NetApp India Pvt. Ltd., Bangalore, India) \\
	\emph{Project}: Workload Characterization Using Trace Segmentation \\
	Development and implementation of a technique for storage workload characterization using time series segmentation and Markov chain modeling \\
	
	\medskip
	
	\textbf {Summer Research Fellow}, \emph{Indian Statistical Institute, Kolkata, India} \hfill \emph{May - Jul 2011} \\
	\emph{Advisor}: Prof. Bidyut Baran Chaudhuri (\url{http://www.isical.ac.in/~bbc}) \\
	\emph{Project}: PageRank-based Single Document Summarization \\
	Development and implementation of a sentence extraction based text summarization technique using PageRank scoring \\
	Online demo: \url{http://lightweightsummarizer.appspot.com}

\end{body}

\smallskip

% \newpage{} % uncomment this line if you want to force a new page

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Publications
\header{Publications}

\begin{body}

	\vspace{14pt}
	Pattisapu Nikhil Priyatam, Ajay Dubey, \textbf{Krish Perumal}, Sai Praneeth, Dharmesh Kakadia and Vasudeva Varma. Seed Selection for Domain-Specific Search. 
\emph{To be presented in Vertical Search Relevance Workshop at 23rd International World Wide Web Conference (WWW 2014)}. Seoul, Korea. \\ \url{http://researchweb.iiit.ac.in/~nikhil.priyatam/Papers/www.pdf}

	\medskip

	\vspace{14pt}
	Nikhil Priyatam, Srinivasan Iyenger, \textbf{Krish Perumal} and Vasudeva Varma. Don't Use a Lot When Little Will Do - Genre Identification Using URLs. 
\emph{In complementary proceedings of 14th International Conference on Intelligent Text Processing and Computational Linguistics (CICLing 2013)} \\ \url{http://bit.ly/genre_cicling_2013}
	
	\medskip
	
	\textbf{Krish Perumal}, Jagan Mohan Ungati, Gaurav Kumar, Nitish Jain, Raj Gaurav and Praveen Ranjan Srivastava. Test Data Generation: A Hybrid Approach Using Cuckoo and Tabu Search. \emph{In Swarm, Evolutionary, and Memetic Computing}, pp. 46-54. Springer Berlin Heidelberg, 2011.\\ \url{http://bit.ly/cuckoo_search_2011}
	
	\medskip
	
	\textbf{Krish Perumal} and Bidyut Baran Chaudhuri. Language Independent Sentence Extraction Based Text Summarization. \emph{Proceedings of ICON-2011: 9th International Conference on Natural Language Processing}, pp. 213-218, Macmillan Publishers, India. \\
	\url{http://bit.ly/krish_icon_2011}
\end{body}

\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Projects
\header{Academic Projects}

\begin{body}
	\vspace{14pt}
	\emph{\textbf{Test Data Generation: A Hybrid Approach Using Cuckoo and Tabu Search}} \\
	Research and development of a test data generation technique using C++ under Prof. Praveen Ranjan Srivastava (Lecturer, Department of Computer
Science and Information Systems, BITS Pilani)
	
	\medskip
	
	\emph{\textbf{Edu-Connect}} \\
	Developed a web application using WAMP (Windows, Apache, MySQL, PHP) to enable professor-student
interaction at educational institutions with features like appointment management and automated
SMS notification

\end{body}

\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Skills
\header{Skills}

\begin{body}
	\vspace{14pt}
	\emph{\textbf{Programming/Scripting:}}{} Expert: Java; Intermediate: MATLAB, Octave, HTML/CSS, LaTeX; Beginner: Javascript, PHP, JSP, Servlets \\
	\medskip
	\emph{\textbf{Web Technologies:}}{} Apache Tomcat, Apache Nutch \\
	\medskip
	\emph{\textbf{Database Management Systems:}}{} MySQL, Oracle, Microsoft Access
\end{body}

\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Achievements
\header{Achievements}

\begin{body}
	\vspace{14pt}
	Rank 1 out of 60 students in the undergraduate class of Information Systems 2012 \\
	Summer Research Fellow of Indian Academy of Sciences in 2011 (research funding for 2 months) \\
	Best Student Award, Mount Carmel School (2007-08) \\
	All India Rank 12 in the All India Erose Open Examination \\
\end{body}

\smallskip


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Leadership activities
\header{Leadership Experience}

\begin{body}
	\vspace{14pt}
	\emph{Director}, People-Process-Culture, Nirmaan Organization (\url{http://www.nirmaan.org}), India (2011) \\
	\emph{Campus Ambassador}, Teach For India (\url{http://www.teachforindia.org}), BITS Pilani (2011) \\
	\emph{Coordinator}, Information Systems Association, BITS Pilani (2010-11) \\
	\emph{President}, Nirmaan Organization, BITS Pilani Chapter (2010) \\
	\emph{School Captain/Head Boy}, Mount Carmel School, New Delhi (2006-07) \\
\end{body}

\end{document}